Short and Mechanized Logical Relation for Dependent Type Theory

### 2024-02-22 paper/paper.tex
Add a conclusion

\section{Conclusion}
\label{sec:conclusion}

>>>>

\section{Conclusion}
\label{sec:conclusion}
In this work, we show a short and mechanized proof of consistency
through proof by logical relation for a fully dependently typed
language with a full universe hierarchy, an intensional identity type,
and large elimination. We show the extensibility of our approach by
proving the existence of $\beta\eta$-normal forms with only small
and mechanical changes to our proof development. Our Coq mechanization
leverages existing Coq libraries for reasoning about metatheory and
general-purpose automation, allowing us to significantly reduce the
verbosity typically associated with mechanized proofs and recover a
declarative proof style that is usually only available in pen and
paper. Our development shows that proof by logical relation for
dependent types should be more accessible since it does not always
require months of effort to implement. We hope our proof can inspire
researchers to more actively mechanize results such as consistency,
normalization for dependent type theory.
